---
title: "Dhirendra"
output: ODI Datasets
---

```{r}
library(dplyr)
library(ggplot2)
```

```{r}
odi = read.csv("C:/Users/Administrator/Desktop/sandisk/D/Self/Datasets/odi-batting.csv")
odi
```
```{r}
summary(odi)
```
## Check the Data Structure 

```{r}
str(odi)
```

# Top 10 Batsman in this dataset

```{r}
library(dplyr)
top_10_batsman = odi%>%group_by(Player)%>%summarise(Total = sum(Runs))%>%arrange(-Total)%>%head(10)
top_10_batsman
```
# Top 10 Ground basic of Runs

```{r}
top_10_ground = odi%>%group_by(Ground)%>% summarise(Total = sum(Runs))%>%arrange(-Total)%>%head(10)
top_10_ground
```

## Top 10 Ground basis of Match

```{r}
Top_10_Ground_Match = odi%>%group_by(Ground)%>%summarise(Total = n())%>%arrange(-Total)%>%head(10)
Top_10_Ground_Match
```


## Top Batsman by Century

```{r}
top_bastsman_cent=odi%>%group_by(Player)%>%summarise(No_of_Cent = sum(Runs>99,na.rm = T))%>%arrange(-No_of_Cent)%>%head(10)

top_bastsman_cent

```
# Player wise:Total Matches, No. Of Centruries, No. of 50s, No. of Duck

```{r}
Total_Player = odi %>% group_by(Player)%>%
  summarise(Tot_Match = n_distinct(MatchDate),
            No_cent = sum(Runs>99, na.rm = TRUE),
            No_Fifty = sum(Runs<99 & Runs>49, na.rm = TRUE),
            No_ducks = sum(Runs==0, na.rm = TRUE)) %>%
  arrange(-No_cent)
Total_Player
```

#Performance of India Aganist all Country

```{r}
India_per = Total_Count = odi %>% 
  filter(Country == "India") %>%
  group_by(Versus) %>%
    summarise(Tot_match_India = n_distinct(MatchDate),
            No_runs = sum(Runs, na.rm = TRUE),
            No_of_Cent = sum(Runs>99, na.rm = TRUE),
            Aver_Runs_Match = round((No_runs/Tot_match_India),2)) %>%arrange(-Tot_match_India)
India_per
```
## For each Player find the highest Score

```{r}
Highest_Runs = odi%>%group_by(Player)%>%summarise(Highest_Runs_Player = max(Runs,na.rm = T))%>%
  arrange(-Highest_Runs_Player)%>%head(10)
Highest_Runs
```

### # Country and Player_Total Runs

```{r}
Double_group = odi%>%
  group_by(Country, Player, Ground)%>%
  summarise(Total.Runs = sum(Runs, na.rm = TRUE))%>% arrange(-Total.Runs)%>% head(10)
Double_group
```

## Now Doing some visualization for better understanding way through ggplot2

```{r}
top_10_batsman = odi%>%group_by(Player)%>%summarise(Total = sum(Runs))%>%arrange(-Total)%>%head(10)
top_10_batsman
```

```{r}
library(ggplot2)

graph_1 = ggplot(top_10_batsman, aes(x = reorder(Player, -Total), y = Total)) +
  geom_bar(stat = "identity", width = .5, aes(fill = Player)) + theme_bw()+theme(axis.text.x = element_text(angle = 90))+labs(title = "Bar Chart", subtitle = "Top 10 Batsman",
                         x= "Player Name", y= "No. of Runs ", caption = "www.google.com")

graph_1

```

```{r}
graph_2 = graph_1+geom_text(aes(label=Total),
                          position = position_dodge(width = .7), vjust = -.25)+
  theme(legend.position = "bottom") +
  theme(legend.key.width = unit(.2, "cm"))+
  theme(legend.title = element_blank())

graph_2
```


















